% ============================================================
% Tài liệu tham khảo (IEEE format)
% ============================================================

\newpage
\phantomsection
\addcontentsline{toc}{section}{TÀI LIỆU THAM KHẢO}
\section*{TÀI LIỆU THAM KHẢO}

\begin{sloppypar}

\begin{enumerate}[label={[\arabic*]}]
    \item J. A. Dean, \textit{Lange's Handbook of Chemistry}, 15th ed. New York, NY, USA: McGraw-Hill, 1999.
    
    \item Engineering ToolBox, ``Overall heat transfer coefficients in heat exchangers,'' 2003. [Online]. Available: \url{https://www.engineeringtoolbox.com/overall-heat-transfer-coefficient-d_434.html}
    
    \item J. Gmehling, U. Onken, and W. Arlt, \textit{Vapor-Liquid Equilibrium Data Collection}, vol. I. Frankfurt, Germany: DECHEMA, 1991.
    
    \item D. W. Green and M. Z. Southard, Eds., \textit{Perry's Chemical Engineers' Handbook}, 9th ed. New York, NY, USA: McGraw-Hill, 2019.
    
    \item F. P. Incropera, D. P. DeWitt, T. L. Bergman, and A. S. Lavine, \textit{Fundamentals of Heat and Mass Transfer}, 7th ed. Hoboken, NJ, USA: Wiley, 2011.
    
    \item KOBOLD Messring GmbH, ``NMC -- Capacitive level meter for liquids datasheet,'' 2021. [Online]. Available: \url{https://www.kobold.com/Capacitive-Level-Meter-NMC}
    
    \item KOBOLD Messring GmbH, ``DPM -- Low volume rotating vane flow meter datasheet,'' 2023. [Online]. Available: \url{https://www.kobold.com/Rotating-Vane-Flow-Meter-DPM}
    
    \item National Institute of Standards and Technology, ``NIST Chemistry WebBook, SRD 69.'' [Online]. Available: \url{https://webbook.nist.gov/}
    
    \item J. R. Rumble, Ed., \textit{CRC Handbook of Chemistry and Physics}, 101st ed. Boca Raton, FL, USA: CRC Press/Taylor \& Francis, 2020.
    
    \item Siemens AG, ``SITRANS P200 for gauge and absolute pressure -- Catalog FI 01,'' 2021. [Online]. Available: \url{https://cache.industry.siemens.com/dl/files/047/109765047/att_1041175/v1/sitransp_p200_p210_p220_fi01_en.pdf}
\end{enumerate}

\end{sloppypar}
